Edge sign prediction in general graphs and Correlation Clustering

### 2017-09-12 intro/use_of_sign_graphs.tex
add 2 refs

   \item[Network science]
      As mentioned in the first Chapter, one early use of signed graphs was to model social
      interactions and given the large body of work on community
      detection~\autocite{FortunatoSurvey10}, it is therefore not surprising that \pcc{} has been
      used to study such networks. For instance, one can extract all the votes of the members of a
      political parliament and form a graph whose nodes are politicians and edge weights quantify how
      much they agree or disagree on various issues they have been voting on. This can be used to
      study various social science questions such as loyalty, leadership, coalitions, political
      crisis and polarization. It has been applied to the European
      parliament~\autocite{Mendonca2015}, Slovenian parliament~\autocite{Jiang2015} and the
      Brazilian parliament~\autocites{BrazilCC17}. This can also be used at international level. For
      instance, by considering a dataset of military alliances and disputes, \textcite{Traag2009}
      cluster countries into blocks that resemble those identified by Huntington in his \emph{Clash
      of Civilizations} book. Another source of data is the vote on resolutions during the United
      Nations General Assembly~\autocite{CommunityUN12}. Finally, one can also study how to exploit
      the information contained within the negative links to enhance the visualization of social
      networks~\autocite{Luca10}. Note however that those three last papers not explicitly use a
      \pcc{} formulation.

>>>>

   \item[Network science]
      As mentioned in the first Chapter, one early use of signed graphs was to model social
      interactions and given the large body of work on community
      detection~\autocite{FortunatoSurvey10}, it is therefore not surprising that \pcc{} has been
      used to study such networks. For instance, one can extract all the votes of the members of a
      political parliament and form a graph whose nodes are politicians and edge weights quantify how
      much they agree or disagree on various issues they have been voting on. This can be used to
      study various social science questions such as loyalty, leadership, coalitions, political
      crisis and polarization. It has been applied to the European
      parliament~\autocite{Mendonca2015}, Slovenian parliament~\autocite{Jiang2015} and the
      Brazilian parliament~\autocites{BrazilCC17}. This can also be used at international level. For
      instance, by considering a dataset of military alliances and disputes, \textcite{Traag2009}
      cluster countries into blocks that resemble those identified by Huntington in his \emph{Clash
      of Civilizations} book. Another source of data is the vote on resolutions during the United
      Nations General Assembly~\autocite{CommunityUN12}. Finally, one can also study how to exploit
      the information contained within the negative links to enhance the visualization of social
      networks~\autocites{Luca10}{drawingSignedGraphs11}. Note however that those four last papers
      not explicitly use a \pcc{} formulation.
